Work Fragmentation in Developer Interaction Data

### 2015-08-07 paper.tex
format change

%% bare_jrnl.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

\documentclass[conference]{IEEEtran}

@@

@@

\IEEEoverridecommandlockouts

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An Empirical Study of Work Fragmentation in Software Evolution Tasks}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
\IEEEauthorblockN{Heider Sanchez$^*$, Romain Robbes$^{\dagger}$} 
\IEEEauthorblockA{
Computer Science Department (DCC) \\
University of Chile, Chile
}

\and
\IEEEauthorblockN{Victor M. Gonzalez$^{\dagger}$}
\IEEEauthorblockA{Department of Computer Science \\ 
Instituto Tecnologico Autonomo de Mexico, Mexico}
\thanks{$^*$ supported by a research grant from CONICYT-Chile}
\thanks{$^{\dagger}$ supported by LACCIR Project RFP1212LAC004}
}

% make the title area
\maketitle

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Work fragmentation, interruptions, interaction data %empirical software engineering, mining software repositories
\end{IEEEkeywords}

% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

>>>>

\documentclass[times]{smrauth}

@@

\def\volumeyear{2016}

@@

\begin{document}
%
\runningheads{H. Sanchez, R. Robbes, L. Cruz, V. Gonzalez}{Work Fragmentation in Developer Interaction Data}

% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{ Work Fragmentation in Developer Interaction Data}

\author{Heider Sanchez$^{\ddagger}$, Romain Robbes$^{\ddagger}$, Luis Carlos Cruz$^{\S}$, Victor M. Gonzalez$^{\S}$}

\address{$^{\ddagger}$: Computer Science Department (DCC), University of Chile, Chile;
$^{\S}$: Instituto Tecnologico Autonomo de Mexico, Mexico}

\corraddr{Romain Robbes (rrobbes@dcc.uchile.cl)}

\maketitle

\footnotetext[2]{All the authors are supported by LACCIR Project RFP2012LAC004\\
H. Sanchez is supported by a research grant from CONICYT-Chile\\
R. Robbes is supported by FONDECYT project \#1151195}

% make the title area

@@

% Note that keywords are not normally used for peerreview papers.
\keywords{Work fragmentation, interruptions, interaction data} %empirical software engineering, mining software repositories

@@
